### 2013-09-20 manuscripts/reply/reply.tex
More work on reply.
Adding work exploring odd Hickerson et al results.
Adding scripts for rescaling invalid posteriors to be on in the
same units of time. Also, adding scripts for performing rejection
and regression on Hickerson et al.'s 80,000 best samples from
the global prior.

Moving some files around and updating figure path in `reply.tex`
accordingly.

@@

\mFigure{../../response-redux/hickerson-et-al-posterior/mean_by_dispersion.pdf}{
    Hickerson et al.'s \citeyear{Hickerson2013} joint posterior.
}{figJointPosteriorHickerson}

>>>>

The empirically guided, narrowest prior of \citet{Hickerson2013} ($\divt{} \sim
U(0,0.1)$) likely excludes the true values for at least some of the Philippine
taxa.
The prior matches posterior of \emph{mean} divergence time and is much
narrower than posterior under two of three priors.

@@

\mFigure{../../response-redux/hickerson-et-al-posterior/hickerson-posterior-1k/mean_by_dispersion.pdf}{
    Hickerson et al.'s \citeyear{Hickerson2013} joint posterior.
}{figJointPosteriorHickerson}
